\begin{frame}  
\frametitle{Bugs?}
\begin{quotation}
The difference between the right word and the almost right word is the difference between lightning and a lightning bug.
\end{quotation}
-- Mark Twain
\end{frame}
 
\begin{frame}
\frametitle{Motivation}
\framesubtitle{The Six Stages of Debugging}
\begin{enumerate}
\item  That can’t happen.
\item  That doesn’t happen on my machine.
\item  That shouldn’t happen.
\item  Why does that happen?
\item  Oh, I see.
\item  How did that ever work?
\end{enumerate}
\end{frame}

 
 
\begin{frame}[fragile]
\frametitle{What are conditional expression bugs?}
\begin{lstlisting}[escapeinside=\[\]]
[\textbf{boolean expression}] ? someValue : someOtherValue;

if ([\textbf{boolean expression}]) {
...
}
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Change of If Condition Expression (IF-CC)}
Kai Pan et al.\footnote{Toward an understanding of bug fix patterns}:
\begin{quotation}
This bug fix change fixes the bug by changing the condition expression of an if
condition. The previous code has a bug in the if condition logic.
\end{quotation}

\vspace{1em}

\begin{lstlisting}
- if (getView().countSelected() == 0) {
+ if (getView().countSelected() <= 1) {
\end{lstlisting}
\end{frame}
  
\begin{frame}[fragile]
\frametitle{What are conditional expression bugs?}
\framesubtitle{Commons Math - MathUtils class}
    
\begin{lstlisting}[escapeinside=\[\]]
411: public static int gcd(int u, int v) {
412:   if ([\textbf{u * v == 0}]) {
413:     return (Math.abs(u) + Math.abs(v));
414:   }
...
\end{lstlisting}

\vspace{2em}

\centering What about \texttt{u=0x00110000} and  \texttt{v=0x01100000}?

\end{frame}

\begin{frame}
\frametitle{Problem I}
\framesubtitle{How does the tool know something is \textit{wrong}?}
\begin{center}
\Huge{404}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Problem I}
\framesubtitle{How does the tool know something is \textit{wrong}?}
Some kind of specification:
\begin{itemize}
 \item Model
 \item Contracts
 \item \textbf{Unit tests}
 \item \dots
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{How does the tool know something is \textit{wrong}?}
\framesubtitle{At least one failing test}
      
      \begin{lstlisting}[escapeinside=\[\]]
assertEquals([\textbf{3 * (1$<<$15)}]
            , gcd(3 * (1<<20), 9 * (1<<15)));
	\end{lstlisting}
\end{frame}

\begin{frame}
\frametitle{No-Pol input}
\begin{itemize}
 \item Java source code.
 \item Unit tests with at least one failing test case.
 \item Dependencies (\textit{classpath}).
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{No-Pol output}
Patched Java source file.
\end{frame}
