\chapter{Introduction}
{\begin{small}%
\begin{flushright}%
\it
Take nothing on its looks; take everything on evidence. \\ There's no better rule. \\
--Charles Dickens
\end{flushright}%
\end{small}%
\vspace{.5cm}}

Our contribution is a novel process that uses an SMT solver to fix conditional bugs.
 This process uses the synthesis technique of \textit{Synthesis of loop-free programs}\cite{Gulwani:2011:SLP:1993316.1993506} to synthesize the correct conditions.
\begin{itemize}
 \item This process handles bugs in \texttt{if} expressions and the ternary operator.
 \item This process handles bugs of the form of missing preconditions. Nobody has ever explicitly addressed this defect class before.
 \item This process supports mainstream object-oriented programming languages and esp. the use of side-effects free unary method calls. In contrast, \textit{SemFix}\cite{Nguyen:2013:SPR:2486788.2486890} only supports arithmetic and boolean expressions in C code.
 \item This process is more lightweight than \textit{SemFix}\cite{Nguyen:2013:SPR:2486788.2486890} because it does not require the use of symbolic execution. One needs less technology and less expertise to implement and run the repair approach.
 \item Our approach is evaluated against real bugs and real test suites. Unlike \textit{SemFix}\cite{Nguyen:2013:SPR:2486788.2486890} which presented the repair of artificial and small-scale bugs, we are able to fix real-scale issues.
\end{itemize}

In addition, we describe a generation pattern for easily feeding an SMT solver in our problem domain.
